# Interactive graph
```{r}
#install.packages("alr4")
library(ggplot2)
library(dplyr)
#install.packages("broom")
library(broom)  
library(tidyverse)
library(alr4)

data(Highway)
str(Highway)

model_1 <- lm(rate ~ trks + acpt, data = Highway)
summary(model_1)

model_2 <- lm(rate ~ slim, data = Highway)
summary(model_2)

full_model <- lm(rate ~ trks + acpt + slim, data = Highway)
summary(full_model)

r2_model_1 <- summary(model_1)$r.squared
r2_model_2 <- summary(model_2)$r.squared
r2_full_model <- summary(full_model)$r.squared

print(r2_model_1)
print(r2_model_2)
print(r2_full_model)

```
We can find that $R^2$ from the model 1 is 0.6326149, $R^2$ from the model 2 is 0.4637387 and $R^2$ from the full model is 0.6773765.
Certainly $R^2$ from the model 1 much more closer to full model. So we can find that trks and acpt are more important in model.
Slim does not significantly improve the model.


b. How much additional variation is explained by the addition of `slim` to model 1?
```{r}
0.6773765-0.6326149
```
 Almost 0.0447616 additional variation is explained by the addition of slim to model 1.
 

c. Create an added variable plot for `slim` and add the best fitting line. (Hint: unlike the example in class, there are *two* other regressors in the problem besides `slim`.)
```{r}
rate_y <- residuals(lm(rate ~ trks + acpt, data = Highway))
slim_x <- residuals(lm(slim ~ trks + acpt, data = Highway))

avp_data <- data.frame(rate_y, slim_x)

ggplot(avp_data, aes(x = slim_x, y = rate_y)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", color = "lightblue") +
  theme_bw()



```

<style>
  * {
    font-family: sans-serif;
  }
</style> 

<div id="plot">
</div>

<script src="https://cdn.jsdelivr.net/npm/d3@7"></script>
<script src="scripts/myscript.js"></script>
